Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-08-11 draft.tex
Polish stats section

%% Shortcuts %%
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\dual}[1]{\tilde{#1}}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\reffig}[1]{fig.~(\ref{fig:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\let\eps\varepsilon
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}

@@

The initial motivation for studying what we wish to call the \emph{Method of Moments}
is the determination of angular observables in the rare decay FCNC-mediated decay
$\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
the method we describe in this letter is general, and it applies to arbitrary
decay or scattering processes. We find a previous work \cite{Dighe:1998vk}
advocates this method chiefly for the determination of angular observables in non-leptonic
$B$ decays, but also mentions the applicability to semileptonic decays. We improve
upon this previous work by studying correlations between the angular observables,
and sources of systematic uncertainties. Moreover, we will show that the method
at hand has two benefits over the usual approach based on likelihood fits. To wit:
\begin{enumerate}
    \item Likelihood fits have convergence problems for a small number of
        events, and can require reparametrizations and/or approximations
        for a successful fit to the signal PDF, see e.g. \cite{Egede:2008uy}.
        The method of moments has no such convergence problems.
    \item The results of likelihood fits suffer from systematic uncertainties
        and systematic bias (see e.g. \cite{Egede:2008uy}), especially in but not limited
        to cases in which the PDFs do not faithfully model the underlying physics. We will
        show that the method of moments does not suffer a very particular type of
        mismodelling that arises from introducing a cutoff in a partial wave expansion.
    \item Using the method of moments, the joint probability distribution of the
        angular observables converges towards a multivariate normal distribution.
        This allows an easy transfer of correlation information from the experiments to
        interested theorists.
\end{enumerate}

@@

It is sensible to refer to the angular observable $S_i$ as the \emph{$f_i$-moment} of the PDF $P$.
We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
In addition, integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int \rmdx{x} P(x) g(x)
\end{equation}
can be approximated \cite{MCSM-2004} by the consistent and unbiased
estimator $\est{E_P[g]}$~\cite[sec. 8.2]{James:2006zz}
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1}^K g(x^{(k)}) \,,\,    x^{(k)} \sim P
\end{equation}
due to the strong law of large numbers for $K \to \infty$, assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$.
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
S_i\rangle$.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \right],
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This reduces the estimation of $\aver{S_i}_{\vec{a},\vec{b}}$ to a
(weighted) counting experiment. In the limit $N \to \infty$, the
central limit theorem (CLT) implies that the random vector
\begin{equation}
  \label{eq:angular-obs-vec}
  \widehat{\vec{S}_{\vec{a},\vec{b}}} \equiv (\aver{S_1}_{\vec{a},\vec{b}}\,, \dots, \aver{S_i}_{\vec{a},\vec{b}}\,,
  \dots)
\end{equation}
 follows a multivariate Gaussian distribution whose mean vector
is approximated by \refeq{bin-importance} and whose covariance is
estimated as
\begin{equation}
    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
In our physics applications, the parameter space is compact and each
$\dual{f}_i$ is bounded. Hence the requisites for the most basic
version of the CLT to hold --- finite mean and covariance of
$\dual{f}_i$ --- are automatically satisfied.  We would like to
emphasize that the sample covariance should \fred{``Should'' as in it
  does in practice? Reference toy studies below} rapidly converge
towards the true covariance matrix.  We propose to declare convergence
\fred{I'd prefer: check that skewness and kurtosis are sufficiently
  small} once estimators for skewness and kurtosis are sufficiently
small,

\begin{equation}
    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \leq B_K\,.
\end{equation}
where the limits $B_S$ and $B_K$ should be determined from process-specific, dedicated toy studies.\\

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
\item The angular observable $\aver{S_i}$ can be determined
  independently of any other observable $\aver{S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} In many of the
  decays of interest, there are only say dozens of events recorded.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
\item The approximate normal distribution allows easier and more
  correct transfer of the information in the data to interested
  theorists for more accurate fits of standard-model and new-physics
  parameters \citeneeded\fred{Our fits and others'?} or for more precise predictions of
  optimized observables; e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as \fred{Could add a sketch. It
    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell \ell$.}
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that
  $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is close or even outside the
  allowed region such that a significant part of the probability mass
  of $\vec{S}$ covers unphysical values. In a Bayesian fit, one would
  take $\mathcal{N}(\vec{S} | \widehat{\vec{S}_{\vec{a},\vec{b}}},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle defined by
  \refeq{constr-ex} to have a well defined problem. This could be
  trivially combined with other independent information in a global
  fit. For a likelihood fit, the constraint needs to be built in by
  the experiment into the analysis of the actual events and the
  resulting likelihood as a function of $\vec{S}$ is distinctly not
  Gaussian. Since experimental collaborations as a whole tend to favor
  data-privacy over accurate use of their results in theorist's
  analyses, the multivariate likelihood is kept secret, and cannot be
  recovered from the numerical value of $\vec{S}$ and the standard
  errors reported in written publications. The theorist then usually
  includes the results as independent measurements with a Gaussian
  distribution and disregards the constraint altogether. This last
  situation is undesirable for both experimentalists and theorists.
  \danny{Two comments:
      \begin{itemize}
      \item We should tune down the ``data privacy'' line of thought. LHCb
      actively works on providing the full likelihood to theorists.
      Rather, we should emphasize that providing the likelihood
      as obtained from the ML-fit is technically much harder (think: profile likelihood,
      since the theorists are not interested in control channels, \dots)
      \item The constraints as described here are \emph{theoretical}
      in nature! If one changes the PDF (e.g. in $B\to K^*\ell^+\ell^-$,
      higher partial waves will have an impact on the shape of the
      \emph{physical region}. Thus, imposing these constraints should
      not be done on the side of the experiment.
      \end{itemize}
  }

@@

Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the pull distribution of the observable.
        All pull distributions can successfully be fitted to a gaussian distribution. As an example, we
        show the pull distributions for the observables $S_5$ and $S_7$ for a SM-like $B\to K^*\ell^+\ell^-$
        decays in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the size of $S_k$. The latter can best be shown
        for the uncertainties of two exampular observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
    \item For all toy studies, we produce plots of their Skewness and their Kurtosis as functions of
        $N$. We find in all cases that the distributions agree. 
    \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
    \item \dots
\end{itemize}
We find that all of the above results show consistenly convergence of the distribution for the angular observables
towards a multivariate normal distribution.

>>>>

%% Shortcuts %%
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\dual}[1]{\tilde{#1}}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\reffig}[1]{fig.~(\ref{fig:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\let\eps\varepsilon
\newcommand{\vecest}[1]{\widehat{\vec{#1}}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}

@@

The initial motivation for studying what we wish to call the \emph{Method of Moments}
is the determination of angular observables in the rare decay FCNC-mediated decay
$\bar{B}\to \bar{K}^*(\to \bar{K}\pi)\ell^+\ell^-$. However, we emphasize that
the method we describe in this letter is general, and it applies to arbitrary
decay or scattering processes. We find a previous work \cite{Dighe:1998vk}
advocates this method chiefly for the determination of angular observables in non-leptonic
$B$ decays, but also mentions the applicability to semileptonic decays. We improve
upon this previous work by studying correlations between the angular observables,
and sources of systematic uncertainties. Moreover, we will show that the method
at hand has two benefits over the usual approach based on likelihood fits. To wit:
\begin{enumerate}
    \item Likelihood fits have convergence problems for a small number of
        events, and can require reparametrizations and/or approximations
        for a successful fit to the signal PDF, see e.g. \cite{Egede:2008uy}.
        The method of moments has no such convergence problems.
    \item The results of likelihood fits suffer from systematic uncertainties
        and systematic bias (see e.g. \cite{Egede:2008uy}), especially in but not limited
        to cases in which the PDFs do not faithfully model the underlying physics. We will
        show that the method of moments does not suffer a very particular type of
        mismodelling that arises from introducing a cutoff in a partial wave expansion.
    \item Using the method of moments, the joint probability distribution of the
        angular observables converges towards a multivariate Gaussian distribution.
        This allows an easy transfer of correlation information from the experiments to
        interested theorists.
\end{enumerate}

@@

It is sensible to refer to the angular observable $S_i$ as the
\emph{$f_i$-moment} of the PDF $P$.  We emphasize that a relation of
type \refeq{det-Pi-analytical} holds for any combination of a density
written as in \refeq{def-P} and an orthonormal basis of angular
functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\

Integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int \rmdx{x} P(x) g(x),
\end{equation}
can be approximated \cite{MCSM-2004} by the consistent and unbiased
estimator $\est{E_P[g]}$~\cite[sec. 8.2]{James:2006zz}
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1}^K g(x^{(k)}) \,,\,    x^{(k)} \sim P
\end{equation}
due to the strong law of large numbers for $K \to \infty$, assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$.
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain observables integrated over certain
bins of $\nuvec$. We define
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & \equiv \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \right],
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
For notational simplicity, let us forget about the $\nuvec$
integration and consider only $S_i$. In the limit $K \to \infty$, the
central limit theorem (CLT) implies that the random vector
\begin{equation}
  \label{eq:angular-obs-vec}
  \vecest{S} \equiv (S_1, \dots, S_i\,,
  \dots)
\end{equation}
follows a multivariate Gaussian distribution $\mathcal{N}( \vec{S},
\widehat{\Sigma})$ centered on the true value $\vec{S}$ with a
covariance estimated as
\begin{equation}
    \cov[S_i,S_j] \to \est{\cov}[{S}_i, {S}_j]
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{ S_i}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{ S_j}\big]\,.
\end{equation}
In our physics applications, the parameter space is compact and each
$\dual{f}_i$ is bounded. Hence the requisites for the most basic
version of the CLT to hold --- finite mean and covariance of
$\dual{f}_i$ --- are automatically satisfied.  We would like to
emphasize that the sample covariance should \fred{``Should'' as in it
  does in practice? Reference toy studies below} rapidly converge
towards the true covariance matrix.  We propose to declare convergence
\fred{I'd prefer: check that skewness and kurtosis are sufficiently
  small} once estimators for skewness and kurtosis are sufficiently
small,

\begin{equation}
    \est{\operatorname{Skew}}[S_i,S_j] \leq B_S\,\,\text{ and }\,\,\est{\kurt}[S_i,S_j] \leq B_K\,.
\end{equation}
where the limits $B_S$ and $B_K$ should be determined from process-specific dedicated toy studies.\\

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
  \item The angular observable ${S_i}$ can be determined
  independently of any other observable ${S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions; in fact,
  one does not even need to be able to explicitly formulate the
  likelihood at all.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} In many of the
  decays of interest, there are only say dozens of events recorded.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
  \item The approximate multivariate Gaussian distribution of $\vecest{S}$
  allows easier and more correct transfer of the information in the
  data to interested theorists for more accurate fits of
  standard-model and new-physics parameters \citeneeded\fred{Our fits
    and others'?} or for more precise predictions of optimized
  observables; e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $K \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as \fred{Could add a sketch. It
    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell
    \ell$.}
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that $\widehat{\vec{S}}$
  is close or even outside the allowed region such that a significant
  part of the probability mass covers unphysical values. In a Bayesian
  fit, one would take $\mathcal{N}(\vecest{S} | \vec{S},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle in the $\vec{S}$ plane
  defined by \refeq{constr-ex} to have a well defined problem. This
  could be trivially combined with other independent information in a
  global fit. Someone with a different physics model might have to
  consider a
  different physical region, and could incorporate it just as easily.\\

  For a likelihood fit, the constraint needs to be part of the
  analysis performed by the experimental collaboration, and the
  resulting likelihood as a function of $\vec{S}$ is distinctly not
  Gaussian.  For experimentalists, communicating such a result has
  proved to be challenging due to technical reasons (data formats,
  size etc.) and the fear that theorists misinterprete the many
  nuisance parameters (from control channels, detector calibrations
  etc.) that are also part of the likelihood. This leads to the
  undesirable situation that that only the mode and standard errors
  are reported, and theorists often include the results as independent
  measurements with a Gaussian distribution and disregard the boundary
  problem altogether.

@@

\fred{$N$ used for the symbol $K$ of section I and II}
Our finding can be summarized as follows:
\begin{itemize}
    \item In all studied cases we observed not a single bias in the pull distribution of the observable.
        All pull distributions can successfully be fitted to a gaussian distribution. As an example, we
        show the pull distributions for the observables $S_5$ and $S_7$ for a SM-like $B\to K^*\ell^+\ell^-$
        decays in \reffig{pulls}.
    \item We study the absolute uncertainty $\sigma_k(N)$ with respect to the angular observable $S_k$
        as a function of the number of simulated events $N$. As expected for a multivariate gaussian
        distribution, we find that the absolute uncertainty is well fitted by
        \begin{equation}
            \sigma_k(N) = \frac{\sigma_k(1)}{\sqrt{N}}
        \end{equation}
        with $\sigma_k(1) = \order{1}$, regardless of the size of $S_k$. The latter can best be shown
        for the uncertainties of two exampular observables. Taking again $S_5$ ($\simeq 27\%$) and $S_7$ ($\simeq 2\%$)
        for SM-like $B\to K^*\ell^+\ell^-$ decays, we show the absolute uncertainty in \reffig{errors}.
    \item For all toy studies, we produce plots of their Skewness and their Kurtosis as functions of
        $N$. We find in all cases that the distributions agree.
    \item \todo{Plot Skewness and Kurtosis for $S_5$ and $S_7$ as functions of $N$.}
    \item \dots
\end{itemize}
We find that all of the above results show consistenly convergence of the distribution for the angular observables
towards a multivariate Gaussian distribution.
